---
title: "fancy_phage"
author: "Hannah E. Houts"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r libs}
library(tidyverse)
```


# Fancy phage

## sourmash gather results
gathering a ihmp-ibd virome against the gutphage database, to select a few phage of interest. 

It might be nice to select 5 phage that are abundant, 5 that are high-medium, and 5 that are about the middle.

```{bash}
#gunzip -c ../grist/outputs.gather_virome/gather/SM_CTTKX.gather.csv.gz
```


```{r, message=FALSE}
gather_og <- read_csv("../grist/outputs.gather_virome/gather/SM_CTTKX.gather.csv")

gather <- gather_og %>%
  separate(name, sep = "\t",into = c("name","database_info"),remove = T) %>%
  relocate(name, f_match, average_abund) %>% 
  arrange(desc(f_match))
#gather

gather %>% 
  filter(
    name %in% c(
      'ivig_358', 
      'uvig_505586', 
      'uvig_264832', 
      'uvig_225190', 
      'uvig_308517', 
      'uvig_389464', 
      'uvig_360436', 
      'uvig_110493', 
      'uvig_52126', 
      'uvig_245649', 
      'uvig_516991', 
      'uvig_219649',
      'uvig_143949', 
      'uvig_96206', 
      'uvig_221329'
    )
  )

```


```{r}
gather %>% 
  filter(name %in% c('ivig_358'))
```



### Top 15 phage

but top 15 what.. f_match, or f_match_orig?

but what is more interesting?
We're heading in the direction of seeing if there is a better match of the phage than is represented in the reference genome. 

So does it make more sense to look at making a "bespoke" version of a phage that is highly abundant, or very closely matching something in the metavirome?

The former is more useful, the latter may be easier. Lets start with the former
- 15 highest abundance 


```{r}
#high_fmatch <- gather %>% 
#  slice_max(f_match,n = 5)
#high_fmatch
```


```{r}
high_abund <- gather %>% 
  slice_max(average_abund, n=15) %>% 
  select(name)
high_abund

```

fifteen_phage.txt - contains these names:
```
ivig_358
uvig_505586
uvig_264832
uvig_225190
uvig_308517
uvig_389464
uvig_360436
uvig_110493
uvig_52126
uvig_245649
uvig_516991
uvig_219649
uvig_143949
uvig_96206
uvig_221329
```

For the snakefile:
```
PHAGES = ['ivig_358', 'uvig_505586', 'uvig_264832', 'uvig_225190', 'uvig_308517', 'uvig_389464', 'uvig_360436', 'uvig_110493', 'uvig_52126', 'uvig_245649', 'uvig_516991', 'uvig_219649', 'uvig_143949', 'uvig_96206', 'uvig_221329']

```

For the config:
```
- ../data/ref_genomes/ivig_358.fa
- ../data/ref_genomes/uvig_505586.fa
- ../data/ref_genomes/uvig_264832.fa
- ../data/ref_genomes/uvig_225190.fa
- ../data/ref_genomes/uvig_308517.fa
- ../data/ref_genomes/uvig_389464.fa
- ../data/ref_genomes/uvig_360436.fa
- ../data/ref_genomes/uvig_110493.fa
- ../data/ref_genomes/uvig_52126.fa
- ../data/ref_genomes/uvig_245649.fa
- ../data/ref_genomes/uvig_516991.fa
- ../data/ref_genomes/uvig_219649.fa
- ../data/ref_genomes/uvig_143949.fa
- ../data/ref_genomes/uvig_96206.fa
- ../data/ref_genomes/uvig_221329.fa

```



## making plots

### load plotting libs & data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(viridisLite)
library(ggpubr)
options(scipen = 999)


df <- read_csv("data/compare.csv", show_col_types = FALSE)
df
```

### shared hashes: nbhd & reference
```{r}
names(df)
head(df)
```


```{r}
df_long <- df %>% 
  arrange(nbhd_num_hashes) %>% 
  pivot_longer(
    c(nbhd_and_ref_shared_hashes,
      ref_num_hashes,nbhd_num_hashes, 
      virome_hits_and_ref_shared_hashes, 
      virome_hits_and_nbhd_shared_hashes, 
      virome_hits_num_hashes
      ), 
    values_to = "hashes", 
    names_to = "hash_type"
    )%>% 
  pivot_longer(
    c(
      ref_in_nbhd, 
      cont_nbhd_in_ref
      ), 
    values_to = "containment", 
    names_to = "containment_type"
    )

df_long
```

```{r}

```

```{r}
# all shared hashes
df_long %>% 
ggplot(aes(x=phage_reference, y = hashes, fill = hash_type)) + 
  geom_col(position = "dodge")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_viridis_d(option = "D") +
  labs(title = "Shared Hashes",
      x = "duo",
      y= "number of shared hashes",
      fill= "Phage Reference Genome")+
  coord_flip()
```

```{r}
df_long %>% distinct(hash_type)
```


```{r}
# just virome_hits_and_ref_shared_hashes, virome hashes, and ref hashes
df_long %>% 
  filter(
    hash_type %in% c(
#      "virome_hits_num_hashes",
      "nbhd_and_ref_shared_hashes",				
      "ref_num_hashes",				
      "nbhd_num_hashes",			
      "virome_hits_and_ref_shared_hashes",			
      "virome_hits_and_nbhd_shared_hashes"
      )			
  )%>% 
ggplot(aes(x=phage_reference, y = hashes, fill = hash_type)) + 
  geom_col(position = "dodge")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_viridis_d(option = "D") +
  labs(title = "Shared Hashes",
      x = "duo",
      y= "number of shared hashes",
      fill= "Phage Reference Genome")+
  facet_grid(~ksize)+
  coord_flip()
```

### shared hashes hits & nbhd
```{r}
df %>% 
  arrange(nbhd_num_hashes) %>% 
#  filter(nbhd_num_hashes>=2000) %>% 
  pivot_longer(c(shared_hashes,ref_num_hashes,nbhd_num_hashes), values_to = "hashes", names_to = "hash_type") %>% 
  pivot_longer(c(cont_ref_in_nbhd, cont_nbhd_in_ref), values_to = "containment", names_to = "containment_type") %>% 
#
#  
  ggplot(aes(x=phage_reference, y = hashes, fill = hash_type)) + 
  geom_col(position = "dodge")+
#
#
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_viridis_d(option = "D") +
  labs(title = "Shared Hashes",
      x = "duo",
      y= "number of shared hashes",
      fill= "Phage Reference Genome")+
  coord_flip()
```


### containment
```{r, warning=FALSE}

df %>% 
#
#
    arrange(nbhd_num_hashes) %>% 
#  filter(nbhd_num_hashes>=2000) %>% 
  pivot_longer(c(shared_hashes,ref_num_hashes,nbhd_num_hashes), values_to = "hashes", names_to = "hash_type") %>% 
  pivot_longer(c(cont_ref_in_nbhd, cont_nbhd_in_ref), values_to = "containment", names_to = "containment_type") %>% 
#
#
  ggplot(aes(x=phage_reference, y = containment, fill = containment_type)) + 
  geom_col(position = "dodge")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  scale_fill_viridis_d(option = "D") +
  labs(title = "Containments",
      x = "phage",
      y= "containment",
      fill= "Phage Reference Genome")+
  coord_flip()
# 
```








